---
title: "Indian_GE_2019_Compare_manifestos_BJP"
author: "Agastya"
date: "May 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

An exploration of Indian General elections.

Indian general elections are conducted every 5 years. With more than a billion people India is world's largest democracy. In addition to the size it being a a multi-party democracy adds to complications when it comes to choices.

As a first experiment trying to gauge the intentions and to provide a quantitative measure of the biggest parties I have carried out a text mining project. I have used the party manifestos to identify what are the most frequently used words. This is a good way of starting off with the analysis.

The manifesto for each party was downloaded from their respective website.
## Install packages
```{r message=FALSE}
# install.packages('wordcloud')
```



## Including libraries
```{r message=FALSE}
library(pdftools)
library(dplyr)
library(tidytext)
library(stringr)
library(wordcloud)
library(ggplot2)
```

## Read the data(pdf files)
```{r}
bjp_pdf = 'data/bjp_manifesto_2019.pdf';
cong_pdf = 'data/congress_manifesto_2019.pdf';
bjp_text <- pdf_text(bjp_pdf); #converts pdf files to text
cong_text <- pdf_text(cong_pdf);
```

## Data conditioning
### this converts the pdf into character for each page. we need to extract the strings out of these characters
```{r}
test <- bjp_text[3]; #read from the third page
clean_separators <- function(input){
  sapply(input, list) %>% 
  str_split("\\r\\n", simplify = F ); ## \\r\\n is the separator in windows
}
test2 <- list(bjp_text);
test2 <- lapply(bjp_text, clean_separators)
```

####Tidying data - convert to tibble
```{r}
temp1 <- clean_separators(bjp_text);
temp2 <- unlist(temp1);
bjp_tib <- tibble(line=1:length(temp2),text=temp2);
table_df <- bjp_tib %>% unnest_tokens(word, text)
table_df <- as.data.frame(table_df);
table_df[20:30,]
table_df1 <- table_df %>% filter(nchar(word)>2) # filter rows that have more than two letter words
bjp_tidy <- table_df1 %>% anti_join(stop_words, by='word')
```


#### Most popular words
```{r}
bjp_tidy %>% count(word, sort = T)
```


## Plots
### bar plot of the most popular words in BJP's manifesto
```{r}
bjp_tidy %>%
  count(word, sort = TRUE) %>%
  filter(n > 30) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()
```

#### wordcloud
```{r}
bjp_tidy %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 100))
```

